### 2014-06-01 ACL2014/system.tex
section 2 edits

\section{Problem Statement}
We are interested in finding out, using a batch process, a \emph{small} set of
neighbor candidates for each query such that: 1) the similarity of any 
query term to a neighbor candidate returned is large and within a user-specified 
similarity threshold ($\tau$). 2) We return an approximate set of neighbor 
candidates with a $100\%$ precision and a large recall.

A naive exact brute force algorithm to solve the above problem: 
1) Compute similarity between each query and all queries in the dataset. 
2) Return all the queries as neighbors, which have similarity affinity within a similarity threshold ($\tau$).

This algorithm is exact as it has both $100\%$ precision and recall. 
However, the algorithm is naive as it is not scalable for hundreds of millions of queries. 
The reason being conducting pairwise computations between all the queries in the dataset involves 
quadratic number of comparisons in the query dataset size. 
For hundreds of millions of queries, it means doing petabytes of comparisons; 
that is  computationally challenging or infeasible even in a distributed setting (such as Hadoop).

>>>>

\section{Problem Statement}
We start with a corpus of user queries being represented as vectors
over some domain (e.g. URLs); similarity between queries is to be measured using cosine between the corresponding
vectors. We are also given a set of queries $Q$. 
We are interested in developing a batch process to return a \emph{small}
set of candidate neighbors for each query $q \in Q$ such that the following
are satisfied: 1) the similarity of any returned candidate to the query $q$ is larger than a user-specified 
similarity threshold $\tau$; 2) the set of candidates returned has a large recall. 
Note that, although we return an approximate set of near neighbors, our requirement forces us to 
return a candidate set that has $100\%$ precision. Our aim is to achieve a large recall, while using
a scalable efficient algorithm.

The exact brute force algorithm to solve the above problem would be to compute
similarities between each $q\in Q$ and all queries in the corpus, and return 
all pairs that have similarities higher than the threshold $\tau$. Computing similarities
for all pairs is computationally infeasible on a single computer even if the size of $Q$ is of the order of few thousands
and the corpus size is hundreds of millions. Even in a distributed setting such as Hadoop, the 
resulting communication needed between machines makes this strategy impractical.

Our aim is to empirically study a set of locality sensitive hashing techniques
that enable us to return a set of candidate neighbors while performing
a much smaller (theoretically \emph{sublinear}) set of comparisons.
